Board games group recomendation using metadata

### 2024-11-30 paper v2/paper v2.tex
feat: defined sections of the paper

@@

\subsection{Figures}

>>>>

\section{Methodology}

The methodology for this project is divided into three main stages: data preprocessing, group making, and recommendation. The first stage consists of reducing the data and selecting the most relevant attributes. The second stage consists of grouping the games based on their characteristics, and the third stage consists of recommending games to groups of players based on their preferences.

\subsection{Data preprocessing}

\subsection{Group making}

\subsection{Recommendation}

\section{Sensitivity Analysis}

\section{Results}

\section{Conclusions}

@@

\section{Figures}
